Joint Satellite Distributions in the Local Group

### 2017-10-04 paper/paper.tex
nuevo orden
updated plot order
+1 paragraph

We find 32 pairs with these conditions. Figure shows the physical 
properties (stellar masses, maximum circular velocities, radial
velocities and separation) in those pairs.

@@

@@

\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:sampling}}
\end{figure*}

@@

\subsection{Satellites in the Local Group}

We build two different kinds of statistics from these satellites
First, we compute the shape and alignments for a varying number of
satellites $11\leq N_{s}\leq 15$ keeping their ranking in
$V_{mag}$/$V_{max}$. 
This allows us to estimate the variation expected by changing the
satellite number. 
The second kind of statistics are computed for a fixed number of
satellites $N_{s}=11$ randomly selected from the top $15$ ranked
satellites. 
We perform this bootstrapping $10$ times for each pair. 
This allows us to estimate the variation expected by randomly sampling
the satellites from a parent distribution.

Figure \ref{fig:sampling} summarized the results.

\subsection{Satellites in the Illustris Simulation}

>>>>

We find 27 pairs with these conditions. Figure shows the physical 
properties (stellar masses, maximum circular velocities, radial
velocities and separation) in those pairs.

@@

\subsection{Satellite samples}

We build two different kinds of statistics from these satellites
First, we compute the shape and alignments for a varying number of
satellites $11\leq N_{s}\leq 15$ keeping their ranking in
$M_V$ or $V_{max}$. 
This allows us to estimate the variation expected by changing the
satellite number. 
The second kind of statistics are computed for a fixed number of
satellites $N_{s}=11$ randomly selected from the top $15$ ranked
satellites. 
We perform this bootstrapping $10$ times for each pair. 
This allows us to estimate the variation expected by randomly sampling
the satellites from a parent distribution.

@@

\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

@@

\subsection{Distributions in the Local Group}

Figure \ref{fig:lg_scatter} summarizes our main results for the
observed LG satellite distributions.
In all panels the diagonal line corresponds to the 1:1 ratio.

Here we can see that the mean values of the \texttt{Ranked} and
\texttt{Bootstrapped} samples are similar within the scatter in each
sample. 
The scatter is itself tends to be larger in the \texttt{Bootstrapped}
sample. 
This allows to stablish the LG uncertainties to be used in the next
sections to compare it against the distributions derived from the
Illustris simulation.

There is a third sample in Figure \ref{fig:lg_scatter}. 
It corresponds to the set of \texttt{Random} points that were generated
by randomizing the angular positions of the satellites in the
\texttt{Bootstrapped} samples. 
This allows us to understand the importance of intrinsic satellite's
radial profile distribution in driving the results.
